Market simulator

### 2020-09-18 analysis/05_market_simulator.Rmd
Finished updating labeling

```{r load-data}
# Gammas of the "everything" model
public_political_social_charity_demo <- read_rds(
  here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

@@

```{r persona-reactive-table}
# Placeholder for persona gammas
per_table <- as.data.frame(matrix(rep(0), nrow = 111))

@@

  # Persona 3
  per_table$per3_value <- 0
  per_table$per3_value[per_table$levels == 'Intercept'] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_national_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_international_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_follow_gov] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_travel_developing] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_pref] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_institution_trust] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_others_charitable] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_worship_attendence] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_charity_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_trust_in_charity] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_amount] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_12] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_personal_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_family_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religious_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_sport_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_art_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_labor_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_environmental_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_professional_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_humanitarian_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_consumer_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_other_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_marital_status] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_education] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_income] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_race] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_age] <- 1
  per_table
})

@@

### Calculating the Persona gammas ###

# Persona 1
persona1 <- persona_data[,2]

# matrix multiplication between persona data and gammas
gamma1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona1)

# Persona 2
persona2 <- persona_data[,3]

# matrix multiplication between persona data and gammas
gamma2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona2)

# Persona 3
persona3 <- persona_data[,4]

# matrix multiplication between persona data and gammas
gamma3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(persona3)

# Organization
org1 <- organization_data[,2]

org2 <- organization_data[,3]

org3 <- organization_data[,4]

org4 <- organization_data[,5]

# Expected utility matrix multiplication between computed persona gammas and org data for persona 1
org1_exp_util1 <- exp(t(org1) %*% as.matrix(gamma1))
org2_exp_util1 <- exp(t(org2) %*% as.matrix(gamma1))
org3_exp_util1 <- exp(t(org3) %*% as.matrix(gamma1))
org4_exp_util1 <- exp(t(org4) %*% as.matrix(gamma1))

# Market Share computation from expected utilities between organization
org1_rate1 <- 100 * org1_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
org2_rate1 <- 100 * org2_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
org3_rate1 <- 100 * org3_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
org4_rate1 <- 100 * org4_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)

@@

<!-- Main page Chart with All Personas -->
Market Share
--------------------------------------

```{r global plot}
renderPlotly({
  org_choice = org_reactive()
  per_choice = per_reactive()

  # Persona 1 
  p_gamma1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  # Expected Utility
  org1_exp_util1 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma1))
  org2_exp_util1 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma1))
  org3_exp_util1 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma1))
  org4_exp_util1 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma1))

  # Market Share
  org1_rate1 <- 100 * org1_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
  org2_rate1 <- 100 * org2_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
  org3_rate1 <- 100 * org3_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)
  org4_rate1 <- 100 * org4_exp_util1/sum(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1)

  # Persona 2
  p_gamma2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])

  # Expected Utility
  org1_exp_util2 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma2))
  org2_exp_util2 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma2))
  org3_exp_util2 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma2))
  org4_exp_util2 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma2))

  # Market Share
  org1_rate2 <- 100 * org1_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
  org2_rate2 <- 100 * org2_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
  org3_rate2 <- 100 * org3_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)
  org4_rate2 <- 100 * org4_exp_util2/sum(org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2)

  # Persona 3
  p_gamma3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])

  # Expected Utility
  org1_exp_util3 <- exp(t(org_choice[, 3]) %*% as.matrix(p_gamma3))
  org2_exp_util3 <- exp(t(org_choice[, 4]) %*% as.matrix(p_gamma3))
  org3_exp_util3 <- exp(t(org_choice[, 5]) %*% as.matrix(p_gamma3))
  org4_exp_util3 <- exp(t(org_choice[, 6]) %*% as.matrix(p_gamma3))

  # Market Share
  org1_rate3 <- 100 * org1_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
  org2_rate3 <- 100 * org2_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
  org3_rate3 <- 100 * org3_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)
  org4_rate3 <- 100 * org4_exp_util3/sum(org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3)

  # Data for Plotly
  data <- c(org1_exp_util1, org2_exp_util1, org3_exp_util1, org4_exp_util1, org1_rate1, org2_rate1, org3_rate1, org4_rate1, 
            org1_exp_util2, org2_exp_util2, org3_exp_util2, org4_exp_util2, org1_rate2, org2_rate2, org3_rate2, org4_rate2,
            org1_exp_util3, org2_exp_util3, org3_exp_util3, org4_exp_util3, org1_rate3, org2_rate3, org3_rate3, org4_rate3)

  # Empty dataframe
  org_reactive <- as.data.frame(matrix(data, 24, 1))

  # Organization name inputs
  org_reactive[,2] <- c(input$org1_id, input$org2_id, input$org3_id, input$org4_id)
  # Type of value
  org_reactive[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  # Persona name inputs
  org_reactive[,4] <- c(rep(input$per1_id,8), rep(input$per2_id, 8), rep(input$per3_id, 8))

  # Rename columns
  colnames(org_reactive) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(org_reactive %>% 
             # Only care about the Market Share right now
             filter(Type == "Market Share") %>% 
             # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
             mutate(
               Organization = factor(Organization, levels = c(input$org1_id, input$org2_id, input$org3_id, input$org4_id), ordered = TRUE),
               Persona = factor(Persona, levels = c(input$per1_id, input$per2_id, input$per3_id), ordered = TRUE)) %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="", y = "Market Share") + 
             scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
             theme(legend.position = "right",
                   panel.background = element_blank(),
                   panel.grid.major.y = element_line(color = "#D3D3D3"))
    )
})

<!-- Persona and Organizational Tabs -->
Personas And Organizations {.tabset .tabset-fade}
--------------------------------------------------

@@

```{r persona 1 inputs}

textInput("per1_id",
          label = "Persona Name",
          value = "Persona 1",
          placeholder = "Enter Persona Name",
          width = "450px")

selectInput("per1_national_news",
         label = "Follow national news:",
         choices = c("Rarely",
                     "Once a week",
                     "At least once a day"),
         selected = "At least once a day",
         width = "450px")

selectInput("per1_international_news",
         label = "Follow international news:",
         choices = c("Never",
                     "Sometimes",
                     "Always"),
         selected = "Always",
         width = "450px")

selectInput("per1_news_medium",
         label = "Medium to follow news:",
         choices = c("TV",
                     "Print",
                     "Online (not social media)",
                     "Social media",
                     "Radio",
                     "Email newsletter",
                     "News app"),
         multiple = TRUE,
         selected = c("TV", "Print", "Social media"),
         width = "450px")

selectInput("per1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"),
         selected = "Often",
         width = "450px")

#Fix
selectInput("per1_travel_developing",
         label = "Travel to developing country:",
         choices = c("Doesn't travel", "Does travel"),
         selected = "Does travel",
         width = "450px")

selectInput("per1_political_pref",
         label = "Political views from liberal to conservative:",
         choices = c("Extremely liberal",
                     "Somewhat liberal",
                     "Slightly liberal",
                     "Moderate",
                     "Slightly conservative",
                     "Somewhat conservative",
                     "Extremely conservative"),
         selected = "Somewhat liberal",
         width = "450px")

#Fix
selectInput("per1_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all in political institutions",
                     "Very little trust in political institutions",
                     "Little trust in political institutions",
                     "Nuetral trust in political institutions",
                     "Some trust in political institutions",
                     "A lot of trust in political institutions",
                     "Complete trust in political institutions"),
         selected = "Complete trust in political institutions",
         width = "450px")

selectInput("per1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree",
         width = "450px")

# Fix
selectInput("per1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely attend services",
                     "Attend at least once a month"),
         selected = "Attend at least once a month",
         width = "450px")

selectInput("per1_religion_importance",
         label = "Importance of religion:",
         choices = c("Not important",
                     "Important"),
         selected = "Important",
         width = "450px")

selectInput("per1_religion",
         label = "Religion:",
         choices = c('Catholic',
                     'Protestant',
                     'Christian Orthodox',
                     'Jewish',
                     'Muslim',
                     'Sikh',
                     'Hindu',
                     'Buddhist',
                     'Atheist',
                     'Other (Religion)'),
         selected = 'Protestant',
         width = "450px")

selectInput("per1_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant",
          width = "450px")

#Fix
selectInput("per1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities",
            width = "450px")

>>>>

```{r load-data}
# Gammas of the "everything" model
gammas <- read_rds(
  here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

@@

```{r persona-reactive-table}
# Placeholder for persona reactive table
per_table <- as.data.frame(matrix(rep(0), nrow = nrow(persona_data)))

@@

  # Persona 3
  per_table$per3_value <- 0
  per_table$per3_value[per_table$levels == 'Intercept'] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_national_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_international_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_follow_gov] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_travel_developing] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_pref] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_institution_trust] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_others_charitable] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_worship_attendence] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_charity_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_trust_in_charity] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_amount] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_12] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_personal_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_family_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religious_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_sport_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_art_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_labor_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_environmental_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_professional_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_humanitarian_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_consumer_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_other_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_marital_status] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_education] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_income] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_race] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_age] <- 1
  per_table
})
```

@@

# ### Calculating the Persona gammas ###
# 
# # Persona 1
# persona1 <- persona_data[,2]
# 
# # matrix multiplication between persona data and gammas
# gamma1 <- as.matrix(gammas) %*% as.matrix(persona1)
# 
# 
# # Persona 2
# persona2 <- persona_data[,3]
# 
# # matrix multiplication between persona data and gammas
# gamma2 <- as.matrix(gammas) %*% as.matrix(persona2)
# 
# 
# # Persona 3
# persona3 <- persona_data[,4]
# 
# # matrix multiplication between persona data and gammas
# gamma3 <- as.matrix(gammas) %*% as.matrix(persona3)
# 
# # Organization
# org1 <- organization_data[,2]
# 
# org2 <- organization_data[,3]
# 
# org3 <- organization_data[,4]
# 
# org4 <- organization_data[,5]
# 
# # Expected utility matrix multiplication between computed persona gammas and org data for persona 1
# per1_org1_exp <- exp(t(org1) %*% as.matrix(gamma1))
# per1_org2_exp <- exp(t(org2) %*% as.matrix(gamma1))
# per1_org3_exp <- exp(t(org3) %*% as.matrix(gamma1))
# per1_org4_exp <- exp(t(org4) %*% as.matrix(gamma1))
# 
# # Market Share computation from expected utilities between organization
# per1_org1_share <- 100 * per1_org1_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
# per1_org2_share <- 100 * per1_org2_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
# per1_org3_share <- 100 * per1_org3_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
# per1_org4_share <- 100 * per1_org4_exp/sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)

@@

Market Share
--------------------------------------

```{r compute-and-plot}
# Compute and render the market share plot
renderPlotly({
  org_choice = org_reactive()
  per_choice = per_reactive()

  # Persona 1 predicted betas
  per1_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,3])

  # Persona 1 expected utilities
  per1_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per1_betas))
  per1_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per1_betas))
  per1_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per1_betas))
  per1_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per1_betas))

  # Persona 1 market shares
  per1_share_denom <- sum(per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp)
  per1_org1_share <- 100 * (per1_org1_exp / per1_share_denom)
  per1_org2_share <- 100 * (per1_org2_exp / per1_share_denom)
  per1_org3_share <- 100 * (per1_org3_exp / per1_share_denom)
  per1_org4_share <- 100 * (per1_org4_exp / per1_share_denom)

  # Persona 2 predicted betas
  per2_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,4])

  # Persona 2 expected utilities
  per2_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
  per2_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
  per2_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
  per2_org3_exp <- exp(t(org_choice[,6]) %*% as.matrix(per2_betas))

  # Persona 2 market shares
  per2_share_denom <- sum(per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org3_exp)
  per2_org1_share <- 100 * (per2_org1_exp / per2_share_denom)
  per2_org2_share <- 100 * (per2_org2_exp / per2_share_denom)
  per2_org3_share <- 100 * (per2_org3_exp / per2_share_denom)
  per2_org4_share <- 100 * (per2_org4_exp / per2_share_denom)

  # Persona 3 predicted betas
  per3_betas <- as.matrix(gammas) %*% as.matrix(per_choice[,5])

  # Persona 3 expected utilities
  per3_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per3_betas))
  per3_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per3_betas))
  per3_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per3_betas))
  per3_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per3_betas))

  # Persona 3 market shares
  per3_share_denom <- sum(per3_org1_exp, per3_org2_exp, per3_org3_exp, per3_org4_exp)
  per3_org1_share <- 100 * (per3_org1_exp / per3_share_denom)
  per3_org2_share <- 100 * (per3_org2_exp / per3_share_denom)
  per3_org3_share <- 100 * (per3_org3_exp / per3_share_denom)
  per3_org4_share <- 100 * (per3_org4_exp / per3_share_denom)

  # Data for plotly
  data <- c(
    # Persona 1
    per1_org1_exp, per1_org2_exp, per1_org3_exp, per1_org4_exp, 
    per1_org1_share, per1_org2_share, per1_org3_share, per1_org4_share, 
    # Persona 2
    per2_org1_exp, per2_org2_exp, per2_org3_exp, per2_org3_exp, 
    per2_org1_share, per2_org2_share, per2_org3_share, per2_org4_share,
    # Persona 3
    per3_org1_exp, per3_org2_exp, per3_org3_exp, per3_org4_exp, 
    per3_org1_share, per3_org2_share, per3_org3_share, per3_org4_share
  )

  # Empty organization reactive table
  org_reactive <- as.data.frame(matrix(data, 24, 1))

  # Organization name inputs
  org_reactive[,2] <- c(input$org1_id, input$org2_id, input$org3_id, input$org4_id)
  # Expected utilities and market shares
  org_reactive[,3] <- c(rep('Expected Utility', 4), rep('Market Share', 4))
  # Persona name inputs
  org_reactive[,4] <- c(rep(input$per1_id, 8), rep(input$per2_id, 8), rep(input$per3_id, 8))

  # Rename columns
  colnames(org_reactive) <- c('Value', 'Organization', 'Type', 'Persona')

  ggplotly(
    org_reactive %>% 
      # Only care about the Market Share right now
      filter(Type == "Market Share") %>% 
      # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
      mutate(
        Organization = factor(
          Organization, 
          levels = c(input$org1_id, input$org2_id, input$org3_id, input$org4_id), 
          ordered = TRUE
        ),
        Persona = factor(
          Persona, 
          levels = c(input$per1_id, input$per2_id, input$per3_id), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Organization, fill = Persona)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})
```

Organizations and Personas {.tabset .tabset-fade}
--------------------------------------------------

### Organization 1

```{r org1-inputs}
# Naming
textInput(
  "org1_id",
  label = "Organization Name",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)

# Organization
selectInput(
  "org1_id",
  label = "Select Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  selected = "Red Cross",
  width = "450px"
)

# Issue area
selectInput(
  "org1_issue", 
  label = "Select Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Emergency response",
  width = "450px"
)

# Financial transparency
selectInput(
  "org1_fin_trans",
  label = "Select Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  selected = "Engages in financial transparency",
  width = "450px"
)

# Financial accountability
selectInput(
  "org1_fin_account",
  label = "Select Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  selected = "Engages in financial accountability",
  width = "450px"
)

# Funding sources
selectInput(
  "org1_funding",
  label = "Select Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org1_host_gov",
  label = "Select Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  width = "450px"
)
```

### Organization 2

```{r org2-inputs}
# Naming
textInput(
  "org2_id",
  label = "Organization Name",
  value = "Organization 2",
  placeholder = "Enter Organization Name",
  width = "450px"
)

# Organization
selectInput(
  "org2_id",
  label = "Select Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  selected = "Red Cross",
  width = "450px"
)

# Issue area
selectInput(
  "org2_issue", 
  label = "Select Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Emergency response",
  width = "450px"
)

# Financial transparency
selectInput(
  "org2_fin_trans",
  label = "Select Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  selected = "Engages in financial transparency",
  width = "450px"
)

# Financial accountability
selectInput(
  "org2_fin_account",
  label = "Select Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  selected = "Engages in financial accountability",
  width = "450px"
)

# Funding sources
selectInput(
  "org2_funding",
  label = "Select Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org2_host_gov",
  label = "Select Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  width = "450px"
)
```

### Organization 3

```{r org3-inputs}
# Naming
textInput(
  "org3_id",
  label = "Organization Name",
  value = "Organization 3",
  placeholder = "Enter Organization Name",
  width = "450px"
)

# Organization
selectInput(
  "org3_id",
  label = "Select Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  selected = "Red Cross",
  width = "450px"
)

# Issue area
selectInput(
  "org3_issue", 
  label = "Select Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Emergency response",
  width = "450px"
)

# Financial transparency
selectInput(
  "org3_fin_trans",
  label = "Select Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  selected = "Engages in financial transparency",
  width = "450px"
)

# Financial accountability
selectInput(
  "org3_fin_account",
  label = "Select Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  selected = "Engages in financial accountability",
  width = "450px"
)

# Funding sources
selectInput(
  "org3_funding",
  label = "Select Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org3_host_gov",
  label = "Select Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  width = "450px"
)
```

### Organization 4

```{r org4-inputs}
# Naming
textInput(
  "org4_id",
  label = "Organization Name",
  value = "Organization 4",
  placeholder = "Enter Organization Name",
  width = "450px"
)

# Organization
selectInput(
  "org4_id",
  label = "Select Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  selected = "Red Cross",
  width = "450px"
)

# Issue area
selectInput(
  "org4_issue", 
  label = "Select Issue Area:",
  choices = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  selected = "Emergency response",
  width = "450px"
)

# Financial transparency
selectInput(
  "org4_fin_trans",
  label = "Select Financial Transparency:",
  choices = c("Doesn’t engage in financial transparency", "Engages in financial transparency"),
  selected = "Engages in financial transparency",
  width = "450px"
)

# Financial accountability
selectInput(
  "org4_fin_account",
  label = "Select Financial Accountability:",
  choices = c("Doesn’t engage in financial accountability", "Engages in financial accountability"),
  selected = "Engages in financial accountability",
  width = "450px"
)

# Funding sources
selectInput(
  "org4_funding",
  label = "Select Funding Source:",
  choices = c("Many small private donations", "Handful of wealthy private donors", "Government grants"),
  width = "450px"
)

# Relationship with host government
selectInput(
  "org4_host_gov",
  label = "Select Relationship With Host Government",
  choices = c("Friendly relationship with government", "Criticized by government",  "Under government crackdown"),
  width = "450px"
)
```

@@

```{r per1-inputs}
# Naming
textInput(
  "per1_id",
  label = "Persona Name",
  value = "Persona 1",
  placeholder = "Enter Persona Name",
  width = "450px"
)

# Follow national news
selectInput(
  "per1_national_news",
  label = "Follow national news:",
  choices = c("Rarely", "Once a week", "At least once a day"),
  selected = "At least once a day",
  width = "450px"
)

# Follow international news
selectInput(
  "per1_international_news",
  label = "Follow international news:",
  choices = c("Never", "Sometimes", "Always"),
  selected = "Always",
  width = "450px"
)

# Mediums to follow news
selectInput(
  "per1_news_medium",
  label = "Medium to follow news:",
  choices = c(
    "TV",
    "Print",
    "Online (not social media)",
    "Social media",
    "Radio",
    "Email newsletter",
    "News app"
  ),
  multiple = TRUE,
  selected = c("TV", "Print", "Social media"),
  width = "450px"
)

# Follow government and public affairs
selectInput(
  "per1_follow_gov",
  label = "Follow government & public affairs:",
  choices = c("Not Often", "Often"),
  selected = "Often",
  width = "450px"
)

# Traveled to a developing country
selectInput(
  "per1_travel_developing",
  label = "Travel to developing country:",
  choices = c("Hasn't traveled to a developing country", "Traveled to a developing country"),
  selected = "Traveled to a developing country",
  width = "450px"
)

# Liberal to Conservative
selectInput(
  "per1_political_pref",
  label = "Political views from liberal to conservative:",
  choices = c(
    "Extremely liberal",
    "Somewhat liberal",
    "Slightly liberal",
    "Moderate",
    "Slightly conservative",
    "Somewhat conservative",
    "Extremely conservative"
  ),
  selected = "Somewhat liberal",
  width = "450px"
)

# Trust in political institutions
selectInput(
  "per1_institution_trust",
  label = "Political institution trust from none to complete:",
  choices = c(
    "No trust at all in political institutions",
    "Very little trust in political institutions",
    "Little trust in political institutions",
    "Neutral trust in political institutions",
    "Some trust in political institutions",
    "A lot of trust in political institutions",
    "Complete trust in political institutions"
  ),
  selected = "Complete trust in political institutions",
  width = "450px"
)

# People should be more charitable
selectInput(
  "per1_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly Disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  selected = "Strongly agree",
  width = "450px"
)

# Religious attendance
selectInput(
  "per1_worship_attendance",
  label = "Worship service attendance:",
  choices = c(
    "Not sure",
    "Rarely attend",
    "Attend at least once a month"
  ),
  selected = "Attend at least once a month",
  width = "450px"
)

# Importance of religion
selectInput(
  "per1_religion_importance",
  label = "Importance of religion:",
  choices = c("Not important", "Important"),
  selected = "Important",
  width = "450px"
)

# Religion
selectInput(
  "per1_religion",
  label = "Religion:",
  choices = c(
    'Catholic',
    'Protestant',
    'Christian Orthodox',
    'Jewish',
    'Muslim',
    'Sikh',
    'Hindu',
    'Buddhist',
    'Atheist',
    'Other religion'
  ),
  selected = 'Protestant',
  width = "450px"
)

# Importance of trusting charities
selectInput(
  "per1_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  selected = "Somewhat unimportant",
  width = "450px"
)

# Trust in charities
selectInput(
  "per1_trust_in_charity",
  label = "Charity Trust:",
  choices = c(
    "No trust at all in charities",
    "Very little trust in charities",
    "Little trust in charities",
    "Neutral trust in charities",
    "Some trust in charities",
    "A lot of trust in charities",
    "Complete trust in charities"
  ),
  selected = "Complete trust in charities",
  width = "450px"
)
